### 2018-07-15 arxiv/paper.tex
Minor typesetting changes.

Since the real-valued SH bases (Equation~\ref{eq:sh_real_basis}) have different definitions for $m<0$, $m=0$ or $m>0$,  we get different projections for $\mathcal{S}^{l,m}$, depending on the sign of $m$. Note that in cases where $L^{l,m}$ would appear with $l<0$ or $|m|>l$, this term is implicitly set to zero.
%\vspace{5in}
%\begin{align}
%&-\frac{1}{2}c^{\scaleto{l-1,m-1}{4pt}}
%\partial_y
%L^{\scaleto{l-1,-m+1}{4pt}}
%%\\
%+\frac{1}{2}d^{\scaleto{l+1,m-1}{4pt}}
%\partial_y
%L^{\scaleto{l+1,-m+1}{4pt}}
%%\\
%-\frac{1}{2}\beta^{\scaleto{m}{4pt}}e^{\scaleto{l-1,m+1}{4pt}}
%\partial_y
%L^{\scaleto{l-1,-m-1}{4pt}}
%\nonumber
%\\&
%+\frac{1}{2}\beta^{\scaleto{m}{4pt}}f^{\scaleto{l+1,m+1}{4pt}}
%\partial_y
%L^{\scaleto{l+1,-m-1}{4pt}}
%%\\
%+\frac{1}{2}\delta_{\scaleto{m\neq -1}{4pt}}c^{\scaleto{l-1,m-1}{4pt}}
%\partial_x
%L^{\scaleto{l-1,m-1}{4pt}}
%\nonumber
%\\&
%-\frac{1}{2}\delta_{\scaleto{m\neq -1}{4pt}}e^{{l-1,m+1}}
%\partial_x
%L^{\scaleto{l-1,m+1}{4pt}}
%%\\
%+\frac{1}{2}f^{\scaleto{l+1,m+1}{4pt}}
%\partial_x
%L^{\scaleto{l+1,m+1}{4pt}}
%%\\
%-\frac{1}{2}d^{\scaleto{l+1,m-1}{4pt}}
%\partial_x
%L^{\scaleto{l+1,m-1}{4pt}}
%\nonumber
%\\&
%+a^{\scaleto{l-1,m}{4pt}}
%\partial_z
%L^{\scaleto{l-1,m}{4pt}}
%%\\
%+b^{\scaleto{l+1,m}{4pt}}
%\partial_z
%L^{\scaleto{l+1,m}{4pt}}
%%\\
%+\sigma_t L^{\scaleto{l,m}{4pt}}
%%\\
%-\sigma_s\lambda_{\scaleto{l}{4pt}}p^{\scaleto{l,0}{4pt}}L^{\scaleto{l,m}{4pt}}
%%\\
%= Q^{\scaleto{l,m}{4pt}}
%\label{eq:rpn_m_<_z}
%\end{align}

For $m=0$ we have
\begin{eqnarray}
&&\frac{1}{\sqrt{2}} \left( 
         c^{\scaleto{l-1,-1}{4pt}} \partial_x L^{\scaleto{l-1,1}{4pt}}
        -d^{\scaleto{l+1,-1}{4pt}} \partial_x L^{\scaleto{l+1,1}{4pt}}  \right)
\nonumber \\
&& \frac{1}{\sqrt{2}} \left(
         c^{\scaleto{l-1,-1}{4pt}} \partial_y L^{\scaleto{l-1,-1}{4pt}}
        -d^{\scaleto{l+1,-1}{4pt}} \partial_y L^{\scaleto{l+1,-1}{4pt}}  \right)
\nonumber \\
&&+ \,a^{\scaleto{l-1,0}{4pt}} \partial_z L^{\scaleto{l-1,0}{4pt}}
  + \,b^{\scaleto{l+1,0}{4pt}} \partial_z L^{\scaleto{l+1,0}{4pt}} 
  +\,\sigma_t L^{\scaleto{l,m}{4pt}}
  -\,\sigma_s \lambda_{\scaleto{l}{4pt}} p^{\scaleto{l,0}{4pt}} L^{\scaleto{l,m}{4pt}}
 = Q^{\scaleto{l,m}{4pt}}\quad .
\label{eq:rpn_m_=_z}
\end{eqnarray}
%and for $m>0$:
%\begin{align}
%&
%\frac{1}{2}c^{\scaleto{l-1,-m-1}{4pt}}\partial_x L^{\scaleto{l-1,m+1}{4pt}}
%%\\&
%-\frac{1}{2}d^{\scaleto{l+1,-m-1}{4pt}}\partial_x L^{\scaleto{l+1,m+1}{4pt}}
%%\\&
%-\frac{1}{2}\beta^{\scaleto{m}{4pt}}e^{\scaleto{l-1,m-1}{4pt}}\partial_x L^{\scaleto{l-1,m-1}{4pt}}
%\nonumber
%\\&
%+\frac{1}{2}\beta^{\scaleto{m}{4pt}}f^{l+1,-m+1}\partial_x L^{\scaleto{l+1,m-1}{4pt}}
%%\\&
%+\frac{1}{2}c^{\scaleto{l-1,-m-1}{4pt}}\partial_y L^{\scaleto{l-1,-m-1}{4pt}}
%\nonumber
%\\&
%-\frac{1}{2}d^{\scaleto{l+1,-m-1}{4pt}}\partial_y L^{\scaleto{l+1,-m-1}{4pt}}
%%\nonumber
%%\\&
%+\delta_{\scaleto{m\neq 1}{4pt}}\frac{1}{2}e^{\scaleto{l-1,-m+1}{4pt}}%\partial_y L^{\scaleto{l-1,-m+1}{4pt}}
%\nonumber
%\\&
%-\delta_{\scaleto{m\neq 1}{4pt}}\frac{1}{2}f^{\scaleto{l+1,-m+1}{4pt}}%\partial_y L^{\scaleto{l+1,-m+1}{4pt}}
%%\\&
%+a^{\scaleto{l-1,-m}{4pt}}\partial_z L^{\scaleto{l-1,m}{4pt}}
%%\nonumber
%%\\&
%+b^{\scaleto{l+1,-m}{4pt}}\partial_z L^{\scaleto{l+1,m}{4pt}}
%\nonumber
%\\&
%+\sigma_t L^{\scaleto{l,m}{4pt}}
%-\sigma_s\lambda_{\scaleto{l}{4pt}}p^{\scaleto{l,0}{4pt}}L^{\scaleto{l,m}{4pt}}
%= Q^{\scaleto{l,m}{4pt}}
%%\nonumber
%\label{eq:rpn_m_>_z}
%\end{align}

>>>>

Since the real-valued SH bases (Equation~\ref{eq:sh_real_basis}) have different definitions for $m<0$, $m=0$ or $m>0$,  we get different projections for $\mathcal{S}^{l,m}$, depending on the sign of $m$. (Note that in cases where $L^{l,m}$ would appear with $l<0$ or $|m|>l$, this term is implicitly set to zero.)
%\vspace{5in}
%\begin{align}
%&-\frac{1}{2}c^{\scaleto{l-1,m-1}{4pt}}
%\partial_y
%L^{\scaleto{l-1,-m+1}{4pt}}
%%\\
%+\frac{1}{2}d^{\scaleto{l+1,m-1}{4pt}}
%\partial_y
%L^{\scaleto{l+1,-m+1}{4pt}}
%%\\
%-\frac{1}{2}\beta^{\scaleto{m}{4pt}}e^{\scaleto{l-1,m+1}{4pt}}
%\partial_y
%L^{\scaleto{l-1,-m-1}{4pt}}
%\nonumber
%\\&
%+\frac{1}{2}\beta^{\scaleto{m}{4pt}}f^{\scaleto{l+1,m+1}{4pt}}
%\partial_y
%L^{\scaleto{l+1,-m-1}{4pt}}
%%\\
%+\frac{1}{2}\delta_{\scaleto{m\neq -1}{4pt}}c^{\scaleto{l-1,m-1}{4pt}}
%\partial_x
%L^{\scaleto{l-1,m-1}{4pt}}
%\nonumber
%\\&
%-\frac{1}{2}\delta_{\scaleto{m\neq -1}{4pt}}e^{{l-1,m+1}}
%\partial_x
%L^{\scaleto{l-1,m+1}{4pt}}
%%\\
%+\frac{1}{2}f^{\scaleto{l+1,m+1}{4pt}}
%\partial_x
%L^{\scaleto{l+1,m+1}{4pt}}
%%\\
%-\frac{1}{2}d^{\scaleto{l+1,m-1}{4pt}}
%\partial_x
%L^{\scaleto{l+1,m-1}{4pt}}
%\nonumber
%\\&
%+a^{\scaleto{l-1,m}{4pt}}
%\partial_z
%L^{\scaleto{l-1,m}{4pt}}
%%\\
%+b^{\scaleto{l+1,m}{4pt}}
%\partial_z
%L^{\scaleto{l+1,m}{4pt}}
%%\\
%+\sigma_t L^{\scaleto{l,m}{4pt}}
%%\\
%-\sigma_s\lambda_{\scaleto{l}{4pt}}p^{\scaleto{l,0}{4pt}}L^{\scaleto{l,m}{4pt}}
%%\\
%= Q^{\scaleto{l,m}{4pt}}
%\label{eq:rpn_m_<_z}
%\end{align}

For $m=0$ we have
\begin{eqnarray}
&&\frac{1}{\sqrt{2}} \left( 
         c^{\scaleto{l-1,-1}{4pt}} \partial_x L^{\scaleto{l-1,1}{4pt}}
        -d^{\scaleto{l+1,-1}{4pt}} \partial_x L^{\scaleto{l+1,1}{4pt}}  \right)
\nonumber \\
&+& \frac{1}{\sqrt{2}} \left(
         c^{\scaleto{l-1,-1}{4pt}} \partial_y L^{\scaleto{l-1,-1}{4pt}}
        -d^{\scaleto{l+1,-1}{4pt}} \partial_y L^{\scaleto{l+1,-1}{4pt}}  \right)
\nonumber \\
&+& \,a^{\scaleto{l-1,0}{4pt}} \partial_z L^{\scaleto{l-1,0}{4pt}}
  + \,b^{\scaleto{l+1,0}{4pt}} \partial_z L^{\scaleto{l+1,0}{4pt}} 
  +\,\sigma_t L^{\scaleto{l,m}{4pt}}
  -\,\sigma_s \lambda_{\scaleto{l}{4pt}} p^{\scaleto{l,0}{4pt}} L^{\scaleto{l,m}{4pt}}
 = Q^{\scaleto{l,m}{4pt}} \ . \quad
\label{eq:rpn_m_=_z}
\end{eqnarray}
%and for $m>0$:
%\begin{align}
%&
%\frac{1}{2}c^{\scaleto{l-1,-m-1}{4pt}}\partial_x L^{\scaleto{l-1,m+1}{4pt}}
%%\\&
%-\frac{1}{2}d^{\scaleto{l+1,-m-1}{4pt}}\partial_x L^{\scaleto{l+1,m+1}{4pt}}
%%\\&
%-\frac{1}{2}\beta^{\scaleto{m}{4pt}}e^{\scaleto{l-1,m-1}{4pt}}\partial_x L^{\scaleto{l-1,m-1}{4pt}}
%\nonumber
%\\&
%+\frac{1}{2}\beta^{\scaleto{m}{4pt}}f^{l+1,-m+1}\partial_x L^{\scaleto{l+1,m-1}{4pt}}
%%\\&
%+\frac{1}{2}c^{\scaleto{l-1,-m-1}{4pt}}\partial_y L^{\scaleto{l-1,-m-1}{4pt}}
%\nonumber
%\\&
%-\frac{1}{2}d^{\scaleto{l+1,-m-1}{4pt}}\partial_y L^{\scaleto{l+1,-m-1}{4pt}}
%%\nonumber
%%\\&
%+\delta_{\scaleto{m\neq 1}{4pt}}\frac{1}{2}e^{\scaleto{l-1,-m+1}{4pt}}%\partial_y L^{\scaleto{l-1,-m+1}{4pt}}
%\nonumber
%\\&
%-\delta_{\scaleto{m\neq 1}{4pt}}\frac{1}{2}f^{\scaleto{l+1,-m+1}{4pt}}%\partial_y L^{\scaleto{l+1,-m+1}{4pt}}
%%\\&
%+a^{\scaleto{l-1,-m}{4pt}}\partial_z L^{\scaleto{l-1,m}{4pt}}
%%\nonumber
%%\\&
%+b^{\scaleto{l+1,-m}{4pt}}\partial_z L^{\scaleto{l+1,m}{4pt}}
%\nonumber
%\\&
%+\sigma_t L^{\scaleto{l,m}{4pt}}
%-\sigma_s\lambda_{\scaleto{l}{4pt}}p^{\scaleto{l,0}{4pt}}L^{\scaleto{l,m}{4pt}}
%= Q^{\scaleto{l,m}{4pt}}
%%\nonumber
%\label{eq:rpn_m_>_z}
%\end{align}
